Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-16 chapters/discussion/discussion.tex
minor change

In \chapref{whenwhere}, we constructed the constraint function for 
the image capture time and the camera location. In order to achieve
this goal, we trained a CNN on a large dataset that consists of
millions webcam frames and smart phone photos. The network takes image
as input and output the discrete probability over location and time.
In this work, we took the advantage that geo-tagged and
temporal-tagged images are common nowadays, to build our training set.
We demonstrate that geo-calibrating the camera helps learn image
representations useful for image understanding.

In \chapref{crosstransf}, we exploit the overhead image to construct
the constraint function for the camera orientation and location.

>>>>

In \chapref{whenwhere}, we constructed the constraint function for 
the image capture time and the camera location. In order to achieve
this goal, we trained a CNN on a large dataset that consists of
millions webcam frames and smart phone photos. The network takes image
as input and output the discrete probability over location and time.
In this work, we took the advantage that geo-tagged and
temporal-tagged images are common nowadays to build the training set.
We demonstrate that geo-calibrating the camera helps learn image
representations useful for image understanding.

In \chapref{crosstransf}, we exploit overhead imagery to construct
the constraint function for the camera orientation and location.
We trained a CNN that can estimate the semantic layout of the ground
view image from the overhead image. During training, we learn the
pixel-to-pixel correspondences from the aerial image to the ground. We
project the semantic layout the of the overhead image to the ground
view with the learned correspondence.
When computing the output of the constraint function, we feed the
aerial image of the gien location and orientation to the network. By
comparing the aerial-to-ground with the real layout of the ground
image, we measure the consistency between the two and use
it as the value of our constraint function.
We also demonstrate the efficiency of our method for CNN pre-training
for aerial image segmentation.

This thesis proposed a probability model for image geo-calibration. 
Overall, we hope our work can provide xxx.
